Air cargo load and route planning in pickup and delivery operations

### 2024-01-28 latex/responses.tex
Latex files updated

\usepackage{natbib}
\bibliographystyle{elsarticle-harv}

@@

\begin{itemize}
\item [1.] Node solution times depended on the total volume of candidate items to be loaded in each node in relation to the total items volume to be loaded in the tour.
\item [2.] A new process of determining the {\it Shims} volume thresholds for $eta_1$ and $eta_2$.
\end{itemize}
}

@@

{\color{blue}
We included Table 10 with the results of the {\it iRace} tool, a software package that helps to automatically fine-tune algorithm parameters. We fine-tuned parameters $threshold_1$\/ and $threshold_2$\/, the relative volumes of each pallet used to determine the indexes  $\eta_1$\/ and $\eta_2$ for the {\it Shims} heuristic.
}
	\end{minipage}
\end{center}

@@

This inclusion may have contributed to the slight improvement in the \textit{Shims} results.

@@

{\color{blue}
	After the items were generated, some experiments with the \textit{iRace} tool were executed to determine the values for parameters $threshold_1$ and $threshold_2$ used in \textit{Shims}, whose results are presented in Table \ref{tab:irace}.

	\begin{table}[H]
		\centering
		\caption{\textit{iRace} testing results}  \label{tab:irace}
		\footnotesize
		\begin{tabular}{cccc}
			\toprule
			\textbf{surplus} & \boldm{$threshold_1$} & \boldm{$threshold_2$} & \textbf{time (min)}\\
			\midrule
			1.2& 0.8621 & 1.0539 & 47 \\
			1.5& 0.9199 & 1.1399 & 59 \\
			2.0& 0.9617 & 1.5706 & 63 \\						
			\bottomrule
		\end{tabular}
		\normalsize
	\end{table}

	For these tests, we considered the odd instances (1, 3, 5, 7) as the \textbf{training} set and the even instances (2, 4, 6) as the \textbf{testing} set for the \textit{iRace} runs. We supplied \textit{iRace} for $threshold_1$ determination, the range [0.8, 1.0], and for $threshold_2$, the range [1.0, 2.0]. The number of iterations in each experiment was limited to 3000 executions for \textit{iRace} to have plenty of data for its statistical tests. More detail about these configurations may be found on the \textit{iRace} user guide in {\tt cran.r-project.org/web/packages/irace/irace.pdf}.
}

@@

		{\color{blue}
	We implemented the genetic algorithm with DEAP (Distributed Evolutionary Algorithms in Python), an evolutionary computation framework available at {\tt github.com/deap/deap}. More details can be found in \citep{DEAP_JMLR2012}.

	We used this package to solve a 15-node TSP with success, whose run time was less than 3s, and generated near-optimal solutions.

@@

	Our GA implementation is not complete. Due to performance issues, we did not include the constraints regarding the Weight and Balance Problem or the Pickup and Delivery Problem.

@@

	We increased the number of items to 100, and the number of pallets to 18, but, even adjusting the GA parameters to more generations (2400) and more individuals (1200), DEAP did not generate any feasible solution. The run time of this attempt was around 5 minutes.

@@

	The code implemented is available in {\tt //github.com/celiomesquita/ACLP\_RPDP\_P/blob/main/ga\_deap\_mmkp.py}.

@@

Large chromosome sizes, like 18,000-dimension arrays, can pose significant challenges in using Genetic Algorithms (GA).

@@

Up to this point in time, we had no success solving the ACLPP with DEAP because it included the palletization planning of 200 to 1000 items per node in a set of 18 aircraft pallets.
		}
	\end{minipage}
\end{center}

@@

We implemented the GA with DEAP (Distributed Evolutionary Algorithms in Python), an evolutionary computation framework available in {\tt github.com/deap/deap}. More details can be found in \citep{DEAP_JMLR2012}.

@@

The code implemented is available in {\tt //github.com/celiomesquita/ACLP\_RPDP\_P/blob/main/tsp\_deap.py}.

@@

The airports cited in Figure \ref{fig:brazil}  are: São Paulo (GRU), Congonhas (CGH), Curitiba (CWB), Porto Alegre (POA), Florianópolis (FLN),  Vitória (VIX), Salvador (SSA), Recife (REC), Fortaleza (FOR), Belém (BEL), Manaus (MAO), Brasília (BSB), Goiânia (GYN), Confins (CNF), and Rio de Janeiro (GIG), returning to GRU.			
		}
	\end{minipage}
\end{center}

\bibliographystyle{apalike}

>>>>

\usepackage{natbib}
%\bibliographystyle{elsarticle-harv}
\bibliographystyle{apalike}

@@

@@

	\begin{itemize}
		\item [1.] Node solution times depended on the total volume of candidate items to be loaded in each node in relation to the total items volume to be loaded in the tour.
		\item [2.] A new process of determining the {\it Shims} volume thresholds for $eta_1$ and $eta_2$.
	\end{itemize}

	We included Table 10 with the results of the {\it iRace} tool, a software package that helps to automatically fine-tune algorithm parameters. We fine-tuned parameters $threshold_1$\/ and $threshold_2$\/, the relative volumes of each pallet used to determine the indexes  $\eta_1$\/ and $\eta_2$ for the {\it Shims} heuristic.
}
	\end{minipage}
\end{center}

@@

This inclusion certainly contributed to the slight improvement observed in the results.

@@

{\color{blue}
	After the items were generated, some experiments with the \textit{iRace} tool were executed to determine the values for volume limits $threshold_1$ and $threshold_2$ used in \textit{Shims}, whose results are presented in Table \ref{tab:irace}.

	\begin{table}[H]
		\centering
		\caption{\textit{iRace} testing results}  \label{tab:irace}
		\footnotesize
		\begin{tabular}{cccc}
			\toprule

			\boldm{$surplus$} & \boldm{$threshold_1$} & \boldm{$threshold_2$} & \textbf{run time}\\
			                 & for $\eta_1$          & for $\eta_2$          & (min) \\
			\midrule
			1.2& 0.8621 & 1.0539 & 47 \\
			1.5& 0.9199 & 1.1399 & 59 \\
			2.0& 0.9617 & 1.5706 & 63 \\						
			\bottomrule
		\end{tabular}
		\normalsize
	\end{table}

	For these tests, we considered the odd instances (1, 3, 5, 7) as the \textbf{training} set and the even instances (2, 4, 6) as the \textbf{testing} set for the \textit{iRace} runs. We supplied \textit{iRace} for $threshold_1$ determination, the range [0.8, 1.0], and for $threshold_2$, the range [1.0, 2.0]. The number of iterations in each experiment was limited to 3000 executions for \textit{iRace} to have plenty of data for its statistical tests. More detail about these configurations may be found on the \textit{iRace} user guide in \url{https://cran.r-project.org/web/packages/irace/irace.pdf}.
}

@@

		{\color{blue}
	We implemented the genetic algorithm with DEAP (Distributed Evolutionary Algorithms in Python), an evolutionary computation framework available at \url{https://github.com/deap/deap}. More details can be found in \citep{DEAP_JMLR2012}.

@@

	Our GA implementation is not complete. Due to performance issues, we did not include the constraints regarding the Weight and Balance (WBP) or the Pickup and Delivery (PDP) problems.

@@

	We increased the number of items to 150, and the number of pallets to 18, but, even adjusting the GA parameters to more generations (2400) and more individuals (1200), DEAP did not generate any feasible solution. The run time of this attempt was around 10 minutes.

@@

	The code implemented is available in \url{https://github.com/celiomesquita/ACLP\_RPDP\_P/blob/main/ga\_deap\_mmkp.py}.

@@

	The palletization planning of 200 to 1000 items per node in a set of 18 aircraft pallets may be an inadequate problem to be solved with GA.

Large chromosome sizes, like 18,000-dimension arrays, can pose significant challenges in using genetic algorithms.

@@

We hope that these considerations help justify why we did not include GA as a candidate method to solve the ACLP+RPDP.
		}
	\end{minipage}
\end{center}

@@

We implemented the GA with DEAP (Distributed Evolutionary Algorithms in Python), an evolutionary computation framework available in \url{https://github.com/deap/deap}. More details can be found in \citep{DEAP_JMLR2012}.

@@

The code implemented is available in \url{https://github.com/celiomesquita/ACLP\_RPDP\_P/blob/main/tsp\_deap.py}.

@@

The airports cited in Figure \ref{fig:brazil}  are: São Paulo (GRU), Congonhas (CGH), Curitiba (CWB), Porto Alegre (POA), Florianópolis (FLN), Vitória (VIX), Salvador (SSA), Recife (REC), Fortaleza (FOR), Belém (BEL), Manaus (MAO), Brasília (BSB), Goiânia (GYN), Confins (CNF), and Rio de Janeiro (GIG), returning to GRU.

}
	\end{minipage}
\end{center}
